\vspace{-3em} \textbf{ Mapping stellar surfaces\\ I: Degeneracies in the rotational light curve problem }

### 2021-01-29 paper1/ms.tex
finished paper 2

The goal of this paper is to explore the degeneracies at play in the
stellar surface mapping problem from a theoretical standpoint.
We will focus in particular on two sources of degeneracies: the
null space intrinsic to the mapping from a two-dimensional surface to
a one-dimensional light curve (\S\ref{sec:nullspace})
and the degeneracy due to the unknowability of the true normalization in
single-band photometry (\S\ref{sec:normalization}). Within each section we
will discuss ways to either break these degeneracies or marginalize
over unknowable quantities.
We will focus in particular on the power of ensemble analyses: the
joint analysis of many light curves of statistically ``similar''
stars. We will show that even though individual light curves are not very
constraining, light curves of many stars
observed at different inclinations can uniquely constrain certain
properties of the surfaces of those stars.
%
This idea was recently explored to some extent
in \citet{Morris2020}, who used ensemble analyses to derive constraints on
spot coverage areas as a function of stellar age. However, one of
the main conclusions of the present paper is that
quantities like \textbf{the
    total spot coverage, the typical spot contrast, and the total number of
    spots are not direct observables in single-band photometry.} Instead,
any constraints placed on these quantities, even in the context of
ensemble analyses, are usually driven by the choice of prior and other assumptions.

>>>>

The goal of this paper is to explore the degeneracies at play in the
stellar surface mapping problem from a theoretical standpoint.
We will focus in particular on two sources of degeneracies: the
null space intrinsic to the mapping from a two-dimensional surface to
a one-dimensional light curve (\S\ref{sec:nullspace})
and the degeneracy due to the unknowability of the true normalization in
single-band photometry (\S\ref{sec:normalization}). Within each section we
will discuss ways to either break these degeneracies or marginalize
over unknowable quantities.
We will focus in particular on the power of ensemble analyses: the
joint analysis of many light curves of statistically ``similar''
stars. We will show that even though individual light curves are not very
constraining, light curves of many stars
observed at different inclinations can uniquely constrain certain
properties of the surfaces of those stars.
%
This idea was recently explored to some extent
in \citet{Morris2020}, who used ensemble analyses to derive constraints on
spot coverage areas as a function of stellar age. However, one of
the main conclusions of the present paper is that
quantities like \textbf{the
    total spot coverage and the total number of
    spots are not direct observables in single-band photometry.} Instead,
any constraints placed on these quantities, even in the context of
ensemble analyses, are usually driven by the choice of prior and other assumptions.
